---
title: "Search"
output:
    html_document:
        includes:
            in_header: "styles/favicon.html"
            after_body: "styles/footer.html"
        css: styles/styles.css
        theme: readable
---


<style>

summary {
    font-size: 18px;
}

</style>


```{r include=F}
library(dplyr)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE)
```


The table below is the heart of the CCGD. The given instructions are intended to be a brief overview for using the table. If further detail is necessary, please visit the [**help**](http://hst-ccgd-prd-web.oit.umn.edu/help.html) page.

<details>
  <summary>**Filters** - subset the dataset by relevant parameters</summary>

There are 4 parameters to filter the dataset by:

* **Species**: this table contains gene homology for several species. The human homolog is always visible.
* **Study**: Select for results of a specific study in this field.
* **Cancer**: Narrow results according to the reported disease model in a study.
* **Genes**: Filter using Entrez gene names. Case sensitivity isn't an issue, and names can be comma or line separated.

</details>

<details>

  <summary>**Visibility** - include hidden columns in the table view</summary>
To account for screen dimensions, we don't list every table column by default. Instead, we offer the option to select hidden columns, which is done with the `Column visibility` button.

All columns are included in the download regardless of selection.

</details>

<details>
  <summary>**Legend** - brief descriptions for each column variable</summary>

```{r}
legend <- read.csv("table_app/legend.csv")
kable(legend) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

</details>

<details>
  <summary>**Download** - export table contents with filtered results in csv format</summary>

Results can be exported using the `Download` button on the left. Any filters applied will be reflected in the csv export.

The full table can be retrieved by downloading without any filter parameters.

</details>

***

<iframe src="https://ctastad.shinyapps.io/table_app/" width=100% height=1100px frameborder="0"></iframe>

