---
title: "Docs"
output:
    html_document:
        includes:
        theme: spacelab
        toc: TRUE
        toc_float: TRUE
---

```{r include = F}
knitr::opts_chunk$set(eval = F)
```

ssh swadm keys setup
httpd setup
script setup
backup process
crontab elements

clone git by https
using ssh forwarding https://developer.github.com/v3/guides/using-ssh-agent-forwarding/
upload process

### Directories

* site dir: `/var/www/ccgd/_site`
* project dir: `/var/www/ccgd`
* backup dir:
* site address

### Scripts

There are several scripts within the ccgd which perform the ongoing maintenance of the application.

backup.sh

Frequency: Daily, every time `ccgd_update.sh` is executed.
Requires: existence of the swadm site dir, ssh access to git repo
Executed: server-side

Arguments: 1st arument supplied will direct the git push to an alternate branch of the repo.

This script performs a full site dir compressions and backup for the Candidate Cancer Gene Database to a site outside the site directory. In addition, it also performs a simple file copy of critical source files. In addition to the backup archive process, this script will also perform a git pull push to update the status of any commits that have been made upstream.

1. Copy the data source files `ccgd_export.csv` and `ccgd_refs.csv` to the back up site.
2. Archive the entire project dir as a tarball and move it to the backup site.
3. Perform a git pull push to the `backup` branch.

build_table.R

build_table.sh

ccgd_upload.sh

./ccgd_upload.sh -b [*FALSE*] -t [*input-file*] -r [*input-file*] -s [*FALSE*] -c [*branch-name*]

Description

With no arguments set, this script will perform a site knit rendering, run `backup.sh`, and execute a git pull-push from the local project directory and on the server-side project directory.


**- b** build

  * Specifies whether to rebuild the table with value *TRUE*. Default is *FALSE*.

**- t** table

  * Option to add new table source file. Argument should be a full directory path to a file named `ccgd_export.csv`.

**- r** refs

  * Option to add new references source file. Argument should be a full directory path to a file named `ccgd_refs.csv`.

**- s** sync

  * Specifies whether to perform a full project directory sync using the `rsync` function with value *TRUE*. Default is *FALSE*.

**- c** checkout

  * Use an alternate git branch in the project directory pull-push. This argument will be passed to the `backup.sh` git pull-push aswell. Default branch used is *backup*.

email_notify.sh

knit_site.R

sanger_pull.sh

### git

* repo: git@github.com:ctastad/ccgd.git

Version control with the git protocol was utilized throughout the development of this application. All components of the ccgd have been tracked, documented, and are now sourced within this repository. In addition to version management, the git transfer protocol plays an important role in the backup and upload process in to maintaining the data accuracy of the application.

#### branches

There are currently 2 branches within the repository which serve standing functions.

##### master

This is the master branch and is intended to carry the common conventions of such. New features should not be pushed to this branch but should instead be developed through the `working` branche and then merged at a point of functional readiness. This branch should be considered the production version of the application.

In addition, because this is the production branch automatic processes direct their commits here as well. The scripts `backup.sh` and `ccgd_update.sh` push to this branch by default. These updates should largely consist of changes to data files like `ccgd_export.csv` and `ccgd_refs.csv`.

##### working

This is the dev branch for the ccgd. The vast majority of the development has taken place on this branch. It should be kept to parity of the master branch at a minimum while there is no active development and should be the home of any future development.

#### ssh keys

* https://developer.github.com/v3/guides/using-ssh-agent-forwarding/

To allow for ssh key use on the server, it is necessary to setup ssh-agent fowarding. This is done by creating a config file at `~/.ssh` that points to the server host. An example of the contents is below.

```{r}
Host hst-ccgd-prd-web.oit.umn.edu
    ForwardAgent yes
```

After this file has been created, run the ssh -T check on the server

```{r}
ssh -T git@github.com
```

https://stackoverflow.com/questions/21906267/ssh-agent-forwarding-configured-and-seems-to-be-working-but-github-still-asks

* importantly, the github remote address needs to be `git@github.com:user/repo.git`.

#### Repo clone

https://help.github.com/en/github/creating-cloning-and-archiving-repositories/cloning-a-repository

clone should be done using https

### copyright

MIT

## RHEL

All changes need to be made under the `swadm` user.

Switching users can be done with the `su` command

```{r}
sudo su swadm
```


### Apache

make sure `httpd.service` is running

```{r}
sudo systemctl start httpd.service
```


config file: `/etc/httpd/conf/httpd.conf`

modified elements of the config file are `DocumentRoot` (line 119) and `<Directory>` (line 131)

any changes made to `httpd.conf` should be followed by a refresh to the system service with the command:

```{r}
sudo systemctl restart httpd.service
```

#### starrnotes

### ssh

Key files are created using the command `ssh-keygen` and are stored in a dot folder under the home directory. The arrangement of server keys should generally be in place for the server setup, but any new client machines would need to go through the process of generating and inserting keys to gain access.

keys should be stored in the swadm .ssh directory: `/home/swadm/.ssh/authorized_keys2`. This can be done by copy-pasting the public ssh key of the client machine at the bottom of this authorized key file on the server.

* !! It is very important that keys are not put in the default `authorized_keys` file. This is wiped by automated OIT processes on a regular basis.
* The correct permissions for the `authorized_keys2` file should be `chmod 600`.

```{r}
-rw-r--r-- 1 swadm swadm    0 Oct 31 19:08 authorized_keys
-rw------- 1 swadm swadm 1464 Nov 26 20:47 authorized_keys2
-rw------- 1 swadm swadm 1675 Dec  2 17:43 id_rsa
-rw-r--r-- 1 swadm swadm  416 Dec  2 17:43 id_rsa.pub
-rw-r--r-- 1 swadm swadm  407 Nov 26 23:08 known_hosts
```

##### ipset

Currently, access to the starrnotes web portal is IP address restricted. To add an allowed address to view starrnotes webpages use the `ipset` command on the server

* https://github.umn.edu/OIT-LPT/Public-Docs/blob/master/ipset.md

```{r}
sudo ipset add http_allowed 128.0.0.0/24
```



### backup

In addition to an archival process outside the project directory, the script `backup.sh` will push the contents of `/swadm/var/www/backup` to a separate server instance outside the ccgd server.
